\myTitle

### 2024-11-06 003-ckmr-sim-evaluation.Rmd
Fix ckmr-comp figure to have the right pop names

AllSims <- tibble(
  condition = input_tibbles$condition,
  ckmr_sim_group = input_tibbles$ckmr_sim_group,
  Qsims = Qsims
) %>% 
  unnest(Qsims) %>%
  select(condition, ckmr_sim_group, true_relat, logl_ratio)
```

Now, we can plot all of those.  Let's see if we can get all four onto one page easily enough.
```{r}
asg <- ggplot(AllSims, aes(x = logl_ratio, fill = true_relat)) +
  geom_density(alpha = 0.5) +
  facet_wrap(~ ckmr_sim_group + condition, ncol = 1) +
  theme_bw() +
  labs(fill = "True\nRelationship") +
  xlab("PO vs U Log-likelihood Ratio")

>>>>

AllSims <- tibble(
  condition = input_tibbles$condition,
  ckmr_sim_group = input_tibbles$ckmr_sim_group,
  Qsims = Qsims
) %>% 
  unnest(Qsims) %>%
  select(condition, ckmr_sim_group, true_relat, logl_ratio) %>%
  mutate(  # change the names around
    group = str_replace(ckmr_sim_group, "^ck-", ""),
    group = case_match(
      group,
      "LF" ~ "CHLF",
      "IGH" ~ "IGHF",
      "SONC" ~ "SO-NCal-Coast",
      "CCC" ~ "Cent-Cal-Coast",
      .default = group
    ),
    .before = ckmr_sim_group
  ) %>%
  mutate(group = factor(group, levels = c("SO-NCal-Coast", "IGHF", "TRH", "Cent-Cal-Coast", "SRW", "BCS", "MDS", "FRH", "CVF", "CHLF")))
```

Now, we can plot all of those.  Let's see if we can get all four onto one page easily enough.
```{r}
asg <- ggplot(AllSims, aes(x = logl_ratio, fill = true_relat)) +
  geom_density(alpha = 0.5) +
  facet_wrap(~ group + condition, ncol = 1) +
  theme_bw() +
  labs(fill = "True\nRelationship") +
  xlab("PO vs U Log-likelihood Ratio")

### 2024-11-06 tex/supplemental-figures.tex
Fix ckmr-comp figure to have the right pop names

%%%%%%%%%%%%%%%%%%%%%% 
\begin{figure}
\begin{center}
\includegraphics[width=0.9\textwidth]{images/cmkr-comp-figure-crop.pdf}
\end{center}
\caption[Comparison of microhaplotypes vs.~best SNP in each amplicon]{\footnotesize 
A comparison of the distribution of log-likelihood ratios when using all the alleles at each
amplicon typed as microhaplotypes ("microhaps" in the panel headers) versus using just a single (the most informative) SNP from each
amplicon ("top\_snps" in the panel headers).  Results shown for four hatchery collections in California 
(ck-FRH: Feather River Hatchery [spring and fall]; ck-IGH: Iron Gate Hatchery; ck-SRW: Sacramento Winter Run;
ck-TRH: Trinity River Hatchery [spring and fall]).  The density plots show
the distribution of log-likelihood ratios for Parent-Offspring vs Unrelated for four different relationships:
PO = parent offspring; FS = full-sibling; HS = Half sibling; AN = avuncular (i.e., aunt-niece, etc.)
The distributions for AN and HS overlap completely.  Note that the overlap between FS and PO occurs
for the PO vs U likelihood ratio, but is nearly eliminated with the PO vs FS likelihood ratio, allowing these
two relationships to be resolved accurately.}
\label{fig:ckmr-comp}
\end{figure}
%%%%%%%%%%%%%%%%%%%%

>>>>

%%%%%%%%%%%%%%%%%%%%%% 
\begin{figure}
\begin{center}
\includegraphics[width=0.9\textwidth]{images/ckmr-comp-figure-crop.pdf}
\end{center}
\caption[Comparison of microhaplotypes vs.~best SNP in each amplicon]{\footnotesize 
A comparison of the distribution of log-likelihood ratios when using all the alleles at each
amplicon typed as microhaplotypes ("microhaps" in the panel headers) versus using just a single (the most informative) SNP from each
amplicon ("top\_snps" in the panel headers).  Results shown for four hatchery collections in California 
(FRH: Feather River Hatchery [spring and fall]; IGH: Iron Gate Hatchery; SRW: Sacramento Winter Run;
TRH: Trinity River Hatchery [spring and fall]).  The density plots show
the distribution of log-likelihood ratios for Parent-Offspring vs Unrelated for four different relationships:
PO = parent offspring; FS = full-sibling; HS = Half sibling; AN = avuncular (i.e., aunt-niece, etc.)
The distributions for AN and HS overlap completely.  Note that the overlap between FS and PO occurs
for the PO vs U likelihood ratio, but is nearly eliminated with the PO vs FS likelihood ratio, allowing these
two relationships to be resolved accurately.}
\label{fig:ckmr-comp}
\end{figure}
%%%%%%%%%%%%%%%%%%%%
